---
title: "UE20CS312 - Data Analytics - Worksheet 1a - part - 2 - EDA with R | ANOVA"
subtitle: "PES University"
author:
- 'Vijay J, Dept. of CSE - PES2UG20CS815'
output: pdf_document
date: "2022-09-01"
urlcolor: blue
editor_options:
markdown:
wrap: 72
---

#**Part I. Exploratory Data Analysis with R**

#**Problem-1**
#Solution
```{r}
library(tidyverse)
library(dbplyr)
library(dplyr)
cbc_df <- read.csv('CharlesBookClubDataset.csv')
sapply(cbc_df[c('X', 'Seq.', 'ID.','Gender','M','R','F','FirstPurch','ChildBks','YouthBks','CookBks','DoItYBks','RefBks','ArtBks','GeogBks','ItalCook','ItalAtlas','ItalArt','Florence','Related.Purchase','Yes_Florence','No_Florence')], sd)
summary(cbc_df)
#Standard Deviation
sapply(cbc_df[c('X', 'Seq.', 'ID.','Gender','M','R','F','FirstPurch','ChildBks','YouthBks','CookBks','DoItYBks','RefBks','ArtBks','GeogBks','ItalCook','ItalAtlas','ItalArt','Florence','Related.Purchase','Yes_Florence','No_Florence')], sd)

```

##To print the number of missing values in each column,
# Number of missing values in each column
```{r}
colSums(is.na(cbc_df))
```

#**Problem-2**
#Solution
```{r}
plot_hist_20_bins <- function() {
  Recency <- cbc_df$R
  Frequency <- cbc_df$F
  Monetary <- cbc_df$M
  hist(Recency, breaks=20)
  hist(Frequency, breaks=20)
  hist(Monetary, breaks=20)
}
plot_hist_20_bins()
```
```{r}
get_mode <- function(x) {
  mode0 <- names(which.max(table(x)))
  if(is.numeric(x)) return(as.numeric(mode0))
  mode0
}

# Apply to all necessary columns

cbc_df$R[is.na(cbc_df$R)] <- get_mode(cbc_df$R)
cbc_df$F[is.na(cbc_df$F)] <- get_mode(cbc_df$F)
cbc_df$M[is.na(cbc_df$M)] <- get_mode(cbc_df$M)
```
##To check our results,
# Number of missing values
```{r}
colSums(is.na(cbc_df))
```
# Plot histograms after imputation
```{r}
plot_hist_20_bins()
```

#**Problem-3**
#Solution

# Create new features that are a result of binning the previous ones

```{r}
cbc_df <- cbc_df %>% mutate(Rcode=cut(cbc_df$R,
                                      breaks=unique(
                                      quantile(cbc_df$R,
                                      probs=seq.int(0,1,by=1/4))),
                                      include.lowest=TRUE),
                                      
                            Mcode=cut(cbc_df$M,
                                      breaks=unique(
                                      quantile(cbc_df$M,
                                      probs=seq.int(0,1,by=1/5))),
                                      include.lowest=TRUE),
                            
                            Fcode=cut(cbc_df$F,
                                      breaks=unique(
                                      quantile(cbc_df$F,
                                      probs=seq.int(0,1,by=1/4))),
                                      include.lowest=TRUE))
```

# Set the level strings
```{r}
levels(cbc_df$Mcode) <- c('$15-$112', '$112-$181', '$181-$242', '$242-$296', '$296-$479')
levels(cbc_df$Rcode) <- c('2-8 months', '8-14 months', '14-16 months', '16-36 months')
levels(cbc_df$Fcode) <- c('1-2 books', '2-6 books', '6-12 books')
```

#Summary
```{r}
summary(cbc_df[c('Mcode', 'Rcode', 'Fcode')])
```


#**Problem-4**
#Solution
#4.1 Bar Graphs

# Bar Graph
```{r}
ggplot(cbc_df, aes(x = Fcode)) + geom_bar() + coord_flip () + labs(x = "Frequency")
ggplot(cbc_df, aes(x = Rcode)) + geom_bar() + coord_flip () + labs(x = "Recency")
ggplot(cbc_df, aes(x = Mcode)) + geom_bar() + coord_flip () + labs(x = "Monetary")
ggplot(cbc_df, aes(x = FirstPurch)) + geom_bar() + coord_flip () + labs(x = "First Purchase")
```

#4.2 Box Plot
# Create a categorical feature Florence
```{r}
cbc_df$Florence <- factor(cbc_df$Florence, labels = c("No", "Yes"))
```
#Box Plot
```{r}
ggplot(cbc_df, aes_string(x = "Florence", y = "R", fill = "Florence")) +
geom_boxplot() +
coord_flip() +
labs(x = "Recency", y = "Did the customer make a purchase?") +
theme(legend.position = c(0.9, 0.9))
```

```{r}
ggplot(cbc_df, aes_string(x = "Florence", y = "M", fill = "Florence")) +
geom_boxplot() +
coord_flip() +
labs(x = "Monetary", y = "Did the customer make a purchase?") +
theme(legend.position = c(0.9, 0.9))
```

```{r}
ggplot(cbc_df, aes_string(x = "Florence", y = "F", fill = "Florence")) +
geom_boxplot() +
coord_flip() +
labs(x = "Frequency", y = "Did the customer make a purchase?") +
theme(legend.position = c(0.9, 0.9))
```

#4.3 Density Plot
#Density Plots

```{r}
ggplot(cbc_df, aes_string(x = "R", fill = "Florence")) +
geom_density(alpha = 0.4) +
labs(x = "Recency") +
theme(legend.position = c(0.9, 0.9))
```

```{r}
ggplot(cbc_df, aes_string(x = "M", fill = "Florence")) +
geom_density(alpha = 0.4) +
labs(x = "Monetary") +
theme(legend.position = c(0.9, 0.9))
```

```{r}
ggplot(cbc_df, aes_string(x = "F", fill = "Florence")) +
geom_density(alpha = 0.4) +
labs(x = "Frequency") +
theme(legend.position = c(0.9, 0.9))
```

##Part II. ANOVA

#**Problem-1**
1. Consider the dataset. Which type of ANOVA can Scully use? (Justify why the particular test)
2. What function(s) could have been used by Scully for ANOVA if he uses the R programming language?
3. What does the output of this/these functions tell Scully? (Specify hypotheses and what each column in
the summary of the output means considering 5% significance)
#Add Libraries and Read CSV

```{r}
library(dplyr)
library(ggplot2)
library(ggpubr)
library(broom)
library(car)

data <- read.csv('Scenario 1.csv')
print(data)
```
#Solution
#1. One-way Anova [Fisher’s test]
#2. aov()
```{r}
scene.1.file <- read.csv('Scenario 1.csv')
one.way <- aov(No.of.items ~ POI, data = scene.1.file)
summary(one.way)
```
#3. Description of each column. Hypotheses of One-way ANOVA test and since p value > 0.05 there is no relation between the person of interest and the average number of evidence collected against them.

#**Problem-2**
1. Consider the data. Which type of ANOVA can Scully use? (Justify why the particular test)
2. What function(s) could have been used by Scully for the ANOVA if he uses the R programming
language?
3. What does the output of this/these functions tell Scully? (Specify hypotheses and what each column in
the summary of the output means considering 5% significance)
4. Hitchcock thinks that Scully has missed a task which completes the ANOVA test. What should Scully
have thought of? Hint: Philosophically, a hypothesis is a proposition made as a basis for reasoning,
without any assumption of its truth.
#Add CSV
```{r}
data <- read.csv('Scenario 2.csv')
```
#Solution
#1. Two-way Anova
#2. aov()
```{r}
scene.2.file <- read.csv('Scenario 2.csv')
two.way <- aov(No.of.items ~ POI * Priority, data = scene.2.file)
summary(two.way)
```
#3. Description of each column. Hypotheses of Two way ANOVA test.
#• since p value < 0.05 there is maybe a relation between the person of interest and the average number of
#evidence collected against them.
#• since p value < 0.05 there is maybe a relation between the Priority and the average number of evidence
#collected against them.
#• Categorical variables cannot be compared with F Statistic and can only be ensured to be independent
#variables by experimental design. (Wrong answer since p value > 0.05 there is no interaction between
#the Priority and person of Interest.)
#4. 3 assumptions of 2 way ANOVA are:
#• Homogeneity of variance (homoscedasticity) [Any one graph with brief explanation on why]
#• Normally-distributed dependent variable
#• Independence of observations: Categorical variables cannot be compared with F Statistic and can
#only be ensured to be independent variables by experimental design. (Wrong answer since p
#value > 0.05 there is no interaction between the Priority and person of Interest.)
```{r}
plot(two.way)
```

```{r}
hist(two.way$residuals,main="Histogram of Residuals",xlab="Residuals")
```

```{r}
hist(scene.2.file$No.of.items,main="Histogram of Dependent Variable",xlab="No of Items")
```

#**Problem-3**
#Solution

```{r}
tukey.two.way<-TukeyHSD(aov(formula = No.of.items ~ factor(POI) + Priority, data = scene.2.file))

tukey.two.way
```

```{r}
par(mar=c(5,8,4,1)+.1)
tukey.plot.test<-TukeyHSD(aov(formula = No.of.items ~ factor(POI), data = scene.2.file))
plot(tukey.plot.test, las = 1)
```

```{r}
par(mar=c(5,8,4,1)+.1)
tukey.plot.test<-TukeyHSD(aov(formula = No.of.items ~ Priority, data = scene.2.file))
plot(tukey.plot.test, las = 1)
```

```{r}
par(mar=c(5,8,4,1)+.1)
tukey.plot.test<-TukeyHSD(aov(formula = No.of.items ~ Priority, data = scene.2.file))
plot(tukey.plot.test, las = 1)
```


